Between-dataset comparisons

### 2019-11-14 analysis/reports/cross_dataset.Rmd
try different di method for bbs
cross dataset report

all_di <- list() 
datasets <- c("bbs", "fia", "gentry", "mcdb", "misc_abund_short", "portal_plants")

@@

 all_di[[i]] <- readd(all_di, cache = cache)
 all_di[[i]] <- filter(all_di[[i]], source == "observed")

>>>>

all_di <- list() 
datasets <- c("bbs", "fia_short", "gentry", "mcdb", "misc_abund_short", "portal_plants")

@@

    all_di[[i]] <- readd(all_di_obs, cache = cache)

  all_di[[i]] <- filter(all_di[[i]], source == "observed")
